Automating the Ontological Argument

### 2015-12-12 Papers/InProgress/IJCAI/paper.tex
minor improvements
Further updates types reinserted in QML_S5 since without types Modal Collapse has a counter example!

\item On a technical level we show that the novel embedding of S5 is more
    effective than the previous one.
\end{itemize}

@@

\section{Automating HOML in HOL}
\subsection{Outline of the Embedding}
\subsection{Improved Embedding for S5}

@@

\subsection{Argument Reconstruction in Isabelle}
Present the argument informal and in Isabelle (see
Fig.~\ref{InconsistencyIsabelleK}). Easy to understand in 
in KB and KT, slightly harder in K.
\begin{figure*}
\centerline{\includegraphics[width=\textwidth]{./Images/InconsistencyIsabelleK.png}}
\caption{Reconstruction of inconsistency in Isabelle/HOl..} \label{InconsistencyIsabelleK}
\end{figure*}

@@

\section{Full Automation of Scott's Proof}
Within the modified logic S5 Scott's proof can be fully automated. The
intermediate argumentation steps as not needed anymore to support the
prover.

>>>>

\item On a technical level we show that the novel embedding of S5 is more
    effective than the previous one.

\item Much improved syntax presentation.

\item Technical issues detected within Isabelle-Sledgehammer; room for improvements
\end{itemize}

@@

\section{Automating HOML in HOL}
\subsection{Outline of the Embedding}
\subsection{Improved Embedding for S5}
We present an improved embedding (syntax and defintion of box) in  Fig.~\ref{QMLS5}).
\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{./Images/QMLS5.png}}
\caption{Improved Embedding of S5} \label{QMLS5}
\end{figure}

\section{Full Automation of Scott's Proof}
Within the modified logic S5 Scott's proof can be fully automated. The
intermediate argumentation steps as not needed anymore to support the
prover, see Fig.~\ref{ScottS5}).
\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{./Images/ScottS5.png}}
\caption{Full Automation of the Ontological Argument in S5} \label{ScottS5}
\end{figure}

@@

\subsection{Argument Reconstruction in Isabelle}
Present the argument informal and in Isabelle (see
Fig.~\ref{InconsistencyIsabelleK}). Easy to understand in 
in KB and KT, slightly harder in K.
\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{./Images/InconsistencyIsabelleK.png}}
\caption{Reconstruction of inconsistency in Isabelle/HOl..} \label{InconsistencyIsabelleK}
\end{figure}

@@
